Thesis Proposal

### 2019-09-30 ThesisProposal.Rmd
Notes MICE meeting

@@

This research project will be supervised by the `MICE` developers. I will develop novel  methodology for evaluating MI data, and implement these methods in an interactive evaluation device in R Shiny [@shiny17]: '`ShinyMICE`'. This approach does not require the use of any empirical data. Therefore, the project is not subject to the school's ethical approval process.

>>>>

**conv te veel nadruk, weinig op diagnostiek, dat is veel sprekender.diag is ook wetenschap, meer modeling dan algorithmisch. in hoeverre duik ik de piepte om conv maat te maken. en aan de andere kant hoe grbruikers helpen om de diagn te maken in mice? bijv kijken of je overimp kunt gebruiken om te zien hoe goed het imp model is. --> double robustness/sensit. analys.**

@@

This research project will be supervised by the `MICE` developers. I will develop novel  methodology for evaluating MI data, and implement these methods in an interactive evaluation device in R Shiny [@shiny17]: '`ShinyMICE`'. This approach does not require the use of any unpublished empirical data. Therefore, the project is not subject to the school's ethical approval process. **or only published data/zonder bewerking van empirische data geen FETC/vrijelijk toegankelijke open access data bewerken vereist ook al FETC misschien?**
